\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

%----------------------------------------------------------------------------------------
%	PERSONAL INFO
%----------------------------------------------------------------------------------------

\name{Ahmad Fajruddin Syauqi}
\address{\href{mailto:fajrudinsauqi@gmail.com}{fajrudinsauqi@gmail.com} \\ \href{tel:+6289699188684}{+6289699188684} \\ \href{https://github.com/syauqiaja/}{github.com/syauqiaja} \\ \href{https://www.linkedin.com/in/fajruddinsyauqi/}{linkedin.com/in/fajruddinsyauqi }}


\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\vspace{0.8em}
\begin{rSection}{Education}

{\bf State University of Malang} \hfill {Sept 2020 - 2024}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Bachelor of Computer Science / Cumulative GPA: 3.88/4.0
\item Relevant Coursework: Data Structure \& Algorithm, Development, Database, Operating System, Computer Organization, System Analyst, Network Security  
 \end{itemize}
 \vspace{-0.5em}
 
 {\bf Djarum Beasiswa Plus} \hfill {Sept 2022 - Aug 2023}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Djarum Foundation Scholarship
\item Relevant Coursework: Leadership, Communication, Analytic, Teamwork, Problem Solving
 \end{itemize}
 \vspace{-0.5em}
 
 {\bf Bangkit Academy} \hfill {Feb 2023 - July 2023}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Mobile Developer Cohort / Graduate with Distinction \href{https://drive.google.com/file/d/1FiU1ONEX-gH2JZHKMGJ98xOr-tF1RwPK/view?usp=drive_link}{[Link]}
\item Relevant Coursework: Mobile Development, UI \& UX Design, Project Management
\item Best Presenter in the Judging Round
 \end{itemize}
 \vspace{-0.5em}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCES SECTION
%----------------------------------------------------------------------------------------
\vspace{0.8em}
\begin{rSection}{EXPERIENCE}

\textbf{Software Developer} \hfill Oct 2024 - Present \\
Galaxy Property \hfill \textit{Surabaya, East Java, Indonesia}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Develop and maintain Galaxy App using Flutter with GetIt and BLoC architecture, improving crash-free user sessions from 58\% to 90\%.
\item Build and manage RESTful APIs and admin web systems using Laravel Livewire, ensuring seamless data integration across platforms.
\item Implement CI/CD pipelines and automation practices, reducing overall development time by 50\% and enhancing release efficiency.
 \end{itemize}
 \vspace{-0.5em}

\textbf{Software Developer} \hfill Sept 2024 - June 2025 \\
Aliflammim \hfill \textit{Kuwait (Remote)}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Led a development team of 3 members in building Kuwait's Quran application using Flutter framework.
\item Implemented robust state management solutions using Provider and BLoC patterns for scalable application architecture.
\item Coordinated team workflows, code reviews, and sprint planning to ensure timely delivery of features.
\item Developed cross-platform mobile application serving Islamic content and Quranic features for Kuwait users.
 \end{itemize}
 \vspace{-0.5em}

\textbf{Android Developer} \hfill Jan 2024 - Jan 2025 \\
Campaign.com \hfill \textit{Jakarta, Indonesia}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Taking responsibility for innovative software architecture and implementing best practices using Kotlin, Java, and Dagger-Hilt.
\item Developing the thank you and profile pages using Coroutines and Asynchronous Flow to optimize multiple API hits, reducing page load time by 50\%.
\item Implement Unit and UI test in JUnit test runner.
\item Hands-on application of cloud messaging, including push notifications and in-app messages.
 \end{itemize}
 \vspace{-0.5em}

\textbf{Founder \& Android Developer} \hfill July 2023 - June 2024
\\ Herbify Indonesia \hfill \textit{Malang, Indonesia}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Reinforce herbify application with RESTful API call and working with JSON.
\item Publish and maintain application on Playstore.
\item Successfully gained 500++ user installs on the first month of Herbify app launching.
 \end{itemize}
 \vspace{-0.5em}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------
\vspace{0.8em}
\begin{rSection}{PROJECTS}
 {\bf Plantelligence} \hfill \href{https://plantelligence.bio}{[Project Link]}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {} 
\item Built an interactive digital flipbook application using Laravel Livewire for real-time rendering and TurnJS for page-turning animations, delivering an enhanced user reading experience.
 \end{itemize}
 \vspace{-0.5em}
 
  {\bf Virulearn} \hfill \href{https://virulearn.com}{[Project Link]}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {} 
\item Developed a Learning Management System in collaboration with Inovasiin.Id to provide interactive virus education for high school students.
\item Implemented responsive UI components using Bootstrap and Laravel Livewire for dynamic, server-side rendered content.
 \end{itemize}
 \vspace{-0.5em}
 
{\bf VRLaboratory} \hfill \href{http://vrlaboratory.bio}{[Project Link]}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Engineered a VR-integrated Learning Management System using Laravel Volt and Tailwind CSS, enabling immersive laboratory simulations.
\item Designed and implemented RESTful API backend services to facilitate seamless communication between the LMS and VR client applications.
\end{itemize}
\vspace{-0.5em}

{\bf Herbify App} \hfill \href{https://play.google.com/store/apps/details?id=com.herbify.herbifyapp&pcampaignid=web_share}{[Project link]}
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item Led Herbal Telemedicine platform development for the herbal industry in Indonesia, leveraging machine learning image classification.
\item Switching from MVVM Architecture to Clean Architecture and implement modularization for 3 weeks to provide a scalable application.
 \end{itemize}
 \vspace{-0.5em}

\end{rSection} 

%----------------------------------------------------------------------------------------
% Achievement SECTION
%----------------------------------------------------------------------------------------
\vspace{0.8em}
\begin{rSection}{Achievement}

\textbf{Top 3 Best Capstone Project - Bangkit Academy 2023 \href{https://drive.google.com/file/d/1rFWcWzdpRQpg781YKZZPdWSyP5ljMyxB/view?usp=drive_link}{[Link]}} \hfill July 2023
\vspace{-0.75em}
\begin{itemize}
\itemsep -7pt {}
\item  Successfully eliminated over 720 participating teams and secured IDR 140 million in funding from Google and Dikti.
\item  Led the development of the Herbify project with a team of 6 members for one month.
 \end{itemize}
 \vspace{-0.5em}
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\vspace{0.8em}
\begin{rSection}{SKILLS}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Mobile Development & Java/Kotlin, Android Studio, Flutter, Dart, MVVM, RxAndroid, JSON, XML  \\
State Management & Provider, BLoC, Coroutines Flow \\
Web Development & HTML, CSS, JS, PHP, TailwindCSS, Laravel, MySQL, PostgreSQL\\
Testing \& Tools & JUnit, Git, Version Control, Dagger-Hilt, CI/CD, PHPUnit\\
Soft Skills & Leadership, Communication, Analytical Skills, Problem Solving, Teamwork \\
\end{tabular}\\
\vspace{-0.75em}
\end{rSection}

\end{document}